Blockchain System

### 2020-12-18 papers/execution-model/model.tex
after discussion: transformed most components into partial maps

A \emph{pending operation} is a tuple
$\langle  \OP, \OPH, \TIME, \STATUSPENDING\rangle $,
where $\OP$ is an operation, $\OPH$ is the operation hash,
and $\TIME$ is the time when the operation was injected.
Once it is accepted, it changes to an \emph{accepted operation}:
$\langle  \OP, \OPH, \TIME, \STATUSINCLUDED\ \TIME'\rangle $, where
$\TIME'$ is the  when it was included in the blockchain.

\begin{definition}%[Blockchain system]
A \emph{blockchain configuration} is a pair
$ \NODE \| \BLOCKCHAIN$ where
\fxnote[inline]{Should the model contain multiple nodes?}
\begin{enumerate}
\item $\NODE = [\ACCOUNTS, \OPERATIONS]$ is the state of a node, and
\item $\BLOCKCHAIN = [\PENDING, \ACCEPTED, \MANAGERS, \CONTRACTORS,
  \TIME]$ is the state of a blockchain  
  such that
  \begin{itemize}
  \item
    $\forall c \in \ACCOUNTS \implies \exists k\in \MANAGERS, k.\PUK =
    c.\PUK$;
  \item 
  \end{itemize}
\end{enumerate}
\end{definition}

>>>>

A \emph{pending operation} is a tuple
$\langle  \OP, \OPH, \TIME, \STATUSPENDING\rangle $,
where $\OP$ is an operation, $\OPH$ is the operation hash,
and $\TIME$ is the time when the operation was injected.
Once it is accepted, it changes to an \emph{accepted operation}:
$\langle  \OP, \OPH, \TIME, \STATUSINCLUDED\ \TIME'\rangle $, where
$\TIME'> \TIME$ is the  when the operation was included in the blockchain.

Properties of blockchain state transitions

\begin{align*}
  P &= \OPH \partialto \OP\times \TIME \times (\STATUSPENDING +
      \STATUSINCLUDED\ \TIME + \STATUSTIMEOUT)
\end{align*}
If $[\PENDING, \MANAGERS, \CONTRACTORS, \TIME] \BlockTrans{}
[\PENDING', \MANAGERS', \CONTRACTORS', \TIME']$, then
\begin{itemize}
\item $\TIME \le \TIME'$
\item $\DOM (\PENDING) \subseteq \DOM(\PENDING')$
\item for all $\OPH \in \DOM(P)$, if  $\PENDING (\OPH) = \Angle{\OP, \TIME, \STATUS}$, then 
  \begin{itemize}
  \item if $\STATUS = \STATUSTIMEOUT$, then $\PENDING'
    (\OPH) = \PENDING (\OPH)$
  \item if $\STATUS = \STATUSINCLUDED\ \TIME'$,
    then $\PENDING'(\OPH) = \PENDING (\OPH)$
  \item if $\STATUS  = \STATUSPENDING$, then either
    \begin{itemize}
    \item % $\BLOCKCHAIN'.\TIME - \TIME \le 60 $ and
      $\PENDING' (\OPH) = \PENDING (\OPH)$
    \item $\PENDING' (\OPH) =       \Angle{\OP, \TIME, \STATUSINCLUDED\ \BLOCKCHAIN.\TIME}$, 
    \item $\BLOCKCHAIN'.\TIME - \TIME > 60$ and $\PENDING' (\OPH) =
      \Angle{\OP, \TIME, \STATUSTIMEOUT}$, 
    \end{itemize}
  \item $ \DOM (\MANAGERS) \subseteq \DOM (\MANAGERS')$
    (Q: can accounts disappear? Do we want to model that?)
  \item for all $\PUK \in \DOM (\MANAGERS)$ if $\MANAGERS (\PUK) =
    \Angle{\BAL, \COU}$ where $\COU = (n, b)$
    \begin{itemize}
    \item if $b= \FALSE$, then $n' = n$
    \item if $b= \TRUE$ and $b'=\TRUE$, then $n' =n$
    \item if $b=\TRUE$ and $b'=\FALSE$, then $n' \in \{ n,  n+1\}$
    \end{itemize}

  \item $ \DOM (\CONTRACTORS) \subseteq \DOM (\CONTRACTORS')$

\begin{definition}%[Blockchain system]
A \emph{blockchain configuration} is a pair
$ \NODE \| \BLOCKCHAIN$ where
\fxnote[inline]{Should the model contain multiple nodes?}
\begin{enumerate}
\item $\NODE = [\ACCOUNTS, \OPERATIONS]$ is the state of a node, and
\item $\BLOCKCHAIN = [\PENDING, \ACCEPTED, \MANAGERS, \CONTRACTORS,
  \TIME]$ is the state of a blockchain  
  such that
  \begin{itemize}
  \item
    $\forall c \in \ACCOUNTS \implies \exists k\in \MANAGERS, k.\PUK =
    c.\PUK$;
  \item if $\PENDING (\OPH) = \Angle{\OP,\TIME, \STATUSINCLUDED\ \TIME'}$,
    then $\TIME' > \TIME$
  \end{itemize}
\end{enumerate}
\end{definition}
